Approximation as Differentiation

### 2025-07-02 main/related-work.tex
Now onto Galois slicing.

More recent approaches to automatic differentiation have emphasised its semantic foundations.
\citet{elliott18} proposed a categorical model of AD that interprets programs not only as functions enriched
with their derivatives, giving a compositional account of differentiation based on duality and linear maps.
This line of work connects AD to denotational semantics, abstracting over operational concerns and enabling
principled extensions to differentiable programming languages. Vákár and
collaborators~\cite{vákár22,nunes2023} developed the CHAD framework, using Grothendieck constructions over
indexed categories to capture both values and their tangents in a unified semantic structure. These semantic
perspectives shed light on the categorical structure of AD and guide the design of systems that generalise
beyond real analysis, including the application to data provenance and slicing explored in this paper.

@@

\cite{berry79,berry82}

>>>>

More recent approaches to automatic differentiation have emphasised its semantic foundations.
\citet{elliott18} proposed a categorical model of AD that interprets programs not only as functions enriched
with their derivatives, giving a compositional account of differentiation based on duality and linear maps.
This line of work connects AD to denotational semantics, abstracting over operational concerns and enabling
principled extensions to differentiable programming languages. Vákár and
collaborators~\cite{vákár22,nunes2023} developed the CHAD framework, using Grothendieck constructions over
indexed categories to capture both values and their tangents in a compositional semantic structure. These
semantic perspectives shed light on the categorical structure of AD and guide the design of systems that
generalise beyond real analysis, including the application to data provenance and slicing explored in this
paper.

@@

\cite{perera12a,perera13,perera16d,ricciotti17,perera22,bond25}
